\bf An Examination of Sport Climbing Competition Format and Scoring System

### 2021-07-30 manuscript/Rmd/draft.tex
Break

>>>>

To the best of our knowledge, we know of no sporting event, team or
individual, that uses the product of ranks to determine an overall
rankings. There are examples of team sports that use the sum of ranks to
determine the winning team such as cross country, where the team with
the lowest sum of ranks of the top five runners is determined to be the
winner. For more detail on rank sum scoring, see \citet{hammond2007} and
\citet{boudreau2018}.

Some individual sports such as the decathlon and heptathlon rely on a
sum of scores from the ten or seven events, however, these scores are
not determined based on the ranks of the competitiors. That is a
decathlete's score is entirely based upon their times, distances, and
heights, and their overall score will be exactly the same if the times,
distances, and heights remain the same regardless of the performance of
other individuals. Full details of dacathlon scoring can be found in
\citet{westera2006}.

There are other individual competitions consisted of several events
combined that do base their scoring on ranks, such as crossfit
competitions. In each event, points are earned based on the competitor's
rank in the event based on a scoring table.
(\url{https://games.crossfit.com/announcement/12940}), and a competitors
final score is based on the sum of their scores across all the events.
